Databrary: Enabling sharing and reuse of research video

### 2015-01-31 jcdl-15/paper.tex
Fix fragment

Sessions provide a container for raw materials and measurements that were made during a data collection \cite{Bakeman_2012}.
As recordings are often the core component of a data collection, a session in many cases is defined by a single recording.
In some cases a single session comprises multiple videos, either serially in time representing different segments or in parallel from multiple cameras recording the same events.
These primary recordings may also be augmented with other forms of timeseries data such as motion capture, eye tracking, or physiological recordings, as well as with additional point-in-time measurements, observations, or surveys. All of which have specific and critical temporal relationships with the primary data.

>>>>

Sessions provide a container for raw materials and measurements that were made during a data collection \cite{Bakeman_2012}.
As recordings are often the core component of a data collection, a session in many cases is defined by a single recording.
In some cases a single session comprises multiple videos, either serially in time representing different segments or in parallel from multiple cameras recording the same events.
These primary recordings may also be augmented with other forms of timeseries data such as motion capture, eye tracking, or physiological recordings, as well as with additional point-in-time measurements, observations, or surveys, all of which have specific and critical temporal relationships with the primary data.
